---
title: "p8105_hw1_yj2686"
author: "Yiqun Jin"
date: "09/27/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:

a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”

```{r data_frame}
df = 
  tibble(
    random_sample = rnorm(10),
    vec_logical = random_sample > 0,
    vec_char = c("a","b","c","d","e","f","g","h","i","j"),
    vec_factor = factor(c("abc","abc","abc","def","def","def","ghi","ghi","ghi","ghi"))
)
```

Try to take the mean of each variable in your data frame. What works and what doesn’t?

ANSWER:

When taking the mean of each variable in data frame, random sample and logical vector worked.
character vector and factor vector did not work and return "Warning in mean.default(df$vec_factor): argument is not numeric or logical: returning NA"

```{r mean_of_variables}
mean(pull(df,random_sample))
mean(pull(df,vec_logical))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))
```
In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

ANSWER:

```{r convert_variables, eval=FALSE}
as.numeric(pull(df,vec_logical))
as.numeric(pull(df,vec_char))
as.numeric(pull(df,vec_factor))
```

When applying as.numeric function, logical vector can converted to 0 and 1; character vector cannot convert to numeric vectors; factor vectors can converted to the number of levels.

##Problem 2

Load penguins datasets

```{r load penguins}
data("penguins", package = "palmerpenguins")
```

Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:

the data in this dataset, including names / values of important variables
the size of the dataset (using nrow and ncol)
the mean flipper length

ANSWER:

The penguins dataset contains `r names(penguins)`
The first variable is `r class(pull(penguins, species))`
The size of the dataset: There are `r nrow(penguins)` rows and `r ncol(penguins)` columns
The mean of flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm = TRUE)`
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
