---
title: "p8105_hw1_yj2686"
author: "Yiqun Jin"
date: "09/27/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:

a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”
Try to take the mean of each variable in your data frame. What works and what doesn’t?

```{r data_frame}
df = 
  tibble(
    random_sample = rnorm(10),
    vec_logical = random_sample > 0,
    vec_char = c("a","b","c","d","e","f","g","h","i","j"),
    vec_factor = factor(c("abc","abc","abc","def","def","def","ghi","ghi","ghi","ghi"))
)
vec_factor = factor(c("abc","abc","abc","def","def","def","ghi","ghi","ghi","ghi"))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
